### 2019-04-01 2015.fall.pku/project1.tex
Add files via upload

\lecture{Project I}{Jinzhu Jia and Yuan Yao}{Due: April 11, 2013}{March 23, 2013}

@@

\begin{enumerate}
\item Pick up ONE (or more if you like) favorite problem below to attack. If you would like to work on a different problem outside the candidates we proposed, please email course instructors about your proposal.  
\item Team work: we encourage you to form small team, up to THREE persons per group, to work on the same problem. Each team just submit ONE report, with a clear remark on each person's contribution. 
\item In the report, show your results with your careful analysis of the results. Remember: scientific analysis and reasoning are more important than merely the performance results. Source codes may be submitted through email as a zip file, or as an appendix if it is not large.    
\item Submit your report by email or paper version no later than the deadline, to Teaching Assistants (TA), Xinyu Chen (\href{mailto:xycbaker@gmail.com}{xycbaker@gmail.com}) and Bowei Yan (\href{mailto:yanbowei@gmail.com}{yanbowei@gmail.com}). 
\end{enumerate}

\section{Problem I (Regression): Keyword Pricing}

@@

\section{Problem II (Classification): click-prediction}

The way to access data is announced in class. Here we give one example for Linux users:
\begin{enumerate}
\item {\texttt{sftp einstein@162.105.68.237}}
\item {\texttt{INPUT your password}}
\item {\texttt{cd /data/ipinyou/}}
\item {\texttt{get all$\_$txt$\_$data.zip}}        \# containing all .txt data files, of size 170MB
\item {\texttt{quit}}
\end{enumerate}

Unzip the file {\texttt{all$\_$txt$\_$data.zip}} to your local directory, you will find the following files:

\begin{itemize}
\item bid.20130301.txt: Bidding log file, 1.2M rows, 470MB
\item imp.20130301.txt: Impression log, 0.8M rows,  360MB
\item clk.20130301.txt: Click log file, 796 rows, 330KB
\item conv.20130301.txt: Conversion log file, 1 rows, 809B.
\item Region\&citys.txt: Region and City code
\item region$\_$en.txt: region name in English
\item region$\_$zh.txt: region name in simplified Chinese
\end{itemize}

\noindent which are just some sample data from iPinyou. Further updates of training data will be released soon. A short introduction on the data format can be found at

\url{http://www.math.pku.edu.cn/teachers/yaoy/Spring2013/dsp_bidding_data_format.pdf}

As a warm-up, the first stage in the DSP-bidding competition is the so called \emph{click-prediction}: find a model to predict the click of impressions. 
To be specific, the file {\texttt{imp.20130301.txt}} (0.8M rows,  360MB) contains 0.8M impressions after winning the bidding, among which only 796 impressions are clicked in the file {\texttt{clk.20130301.txt}} (796 rows, 330KB). The task is to design your features and predict the class of clicks.

For those R users, the following commands can be used to read the data

{\texttt{imp <- read.table("/data/ipinyou/imp.20130301.txt", sep='$\backslash$t', comment.char='')}}

\noindent This is because that R {\texttt{read.table}}Êby default uses '\#' as a comment character, that is, it has {\texttt{comment.char = '\#'}} parameter by default. But the user-agent field in data file may have '\#' character. Hence to read correctly, it is necessary to turn off {\texttt{comment.char=''}}.Ê

One challenge lies in the imbalance of the problem, with 1000 zeroes for a single one. So this is a rare event classification problem. The following paper, Logistic Regression in Rare Events Data, by King and Zeng 2001, might be helpful for you.

\url{http://gking.harvard.edu/files/abs/0s-abs.shtml}

\section{Problem III (Classification): Heart Operation Effect Prediction}

The following data, provided by Dr. Jinwen Wang at Anzhen Hospital,

\url{http://www.math.pku.edu.cn/teachers/yaoy/data/HeartData_20130201.zip}

\noindent contains 2581 patients with 73 measurements (inputs) as well as a response variable indicating if after the heart operation there is a null-reflux state. 
This is a classification problem, with a challenge from the large amount of missing values.

The following two reports by LU, Yu and WANG, Qing, are probably inspiring to you.

\url{http://www.math.pku.edu.cn/teachers/yaoy/reference/LuYu_201303_BigHeart.pdf}

\url{http://www.math.pku.edu.cn/teachers/yaoy/reference/WangQing_201303_BigHeart.pdf}

\end{document}

>>>>

\lecture{Mini-Project 1}{Yuan Yao}{Due: October 12, 2015}{}

@@

\begin{enumerate}
\item Pick up ONE (or more if you like) favorite problem \emph{below} or \emph{from the datasets in textbook} to attack. If you would like to work on a different problem outside the candidates we proposed, please email course instructors about your proposal. Brave hearts for explorations will be encouraged!
\item Team work: we encourage you to form small team, up to FIVE persons per group, to work on the same problem. Each team just submit ONE report. For example a \emph{poster} report, with a clear remark on each person's contribution. A sample poster file with PKU logo can be found at \\
\url{http://www.math.pku.edu.cn/teachers/yaoy/reference/poster_v5.pdf} \\
whose source LATEX codes can be downloaded at \\
\url{http://www.math.pku.edu.cn/teachers/yaoy/reference/pkuposter.zip}
\item In the report, set up your problem to attack and show your results with your analysis. Remember: scientific analysis and reasoning are more important than merely the performance results. Source codes may be submitted through email as a zip file, or as an appendix if it is not large.
\item Submit your report by email or in paper version no later than the deadline, to Teaching Assistants (TA). %   (\href{mailto:statlearning\_hw@126.com}{statlearning\_hw@126.com}). We plan a poster session on Saturday June 21 (evening) for peer reviews.
\end{enumerate}

\section{Animal Species Sleeping Hours Regression}
The following dataset contains $n=51$ species with several features including the average sleeping hours per day.

\url{http://www.math.pku.edu.cn/teachers/yaoy/SummerSchool_2010/sleep1.csv}

Explore \emph{what affects the sleep an animal needs}? A sample R code can be found at

\url{http://www.math.pku.edu.cn/teachers/yaoy/Spring2015/Lecture19.R}

You need to create your own design of analysis.

\section{Crime Rate}
Explore the following dataset about crime rates in 59 US cities during 1970-1992.

\url{http://www.math.pku.edu.cn/teachers/yaoy/data/crime.xlsx}

\section{Keyword Pricing (Regression)}

@@

A reference can be found in Mr. Jiaqi Zhu's bachelor thesis work:

\url{http://www.math.pku.edu.cn/teachers/yaoy/reference/Thesis_ZHUJiaqi.pdf}

\section{Beer Popularity and Rating}

The following data, provided by Mr. Richard (\url{sun.richard@yahoo.com}) from Shanghai,

\url{http://www.math.pku.edu.cn/teachers/yaoy/data/Beers_20140514.xlsx}

\noindent contains 877 brands (rows) of beers in Chinese market, with a few attributes about ingradients, alcoholicity, price (and unit price), reviewers count, mean scores, and as well as sources of reviewers (e.g. amazon, jd, yhd etc.). Two questions are interesting to explore such data

\begin{enumerate}
\item What factors are highly correlated with the popularity of beers indicated by reviewers count?
\item What factors accounts for the mean rating scores? Why are those beers lowly rated?
\end{enumerate}

Note that the data does not contain lots of attributes, so think about your goal before you take a try.

$$ A A^T = A^T A = I $$

$$ AA^T = I \Leftrightarrow \|x\|_2 = \|A^Tx\|_2, \forall x$$

\[ J(A,s) = \|s - A^T x\|_2^2 + \lambda \sqrt{s^2+\epsilon} + \gamma \|A\|_2^2\]

\[ \|A\|_2^2 := trace(A^T A)\]
\end{document}
